Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-10-11 smt/response.tex

\begin{itemize}
\item \textcolor{red}{The paper provides two new ILP formulations for the Shared Multicast Tree (SMT) problem in wireless ad hoc networks.
To address the problem of ILP scalability, the paper also provides a study and proofs of related theorems that shed light on the quality of
solutions achievable by  LP  bounds.
As the number and also provides a new constraint generation scheme.
Numerical results demonstrate the usefulness of the approach. The paper is well written.} \textcolor{blue}{
We are grateful to the reviewer for her/his encouraging remarks, and we appreciate the (s)he finds the paper well written.
}
\item \textcolor{red}{Overall, the methodology makes contribution in the field of optimization as the approach can be used to address other similar problems
that can be modeled as ILP which is not scalable.
However, this paper aims to address the problem of SMT in wireless ad hoc networks and it is
really motivated by the important problem of saving energy in sensor networks.
There I see a certain minor weakness.
The model considered ignores details of energy consumption is sensor network
(see for example Halgamuge et al., Progress in Electromagnetics Research, 12, 2009, or other sources).
It will be good to my opinion to point out this weakness and provide certain qualitative comments to benefit the practitioners,
on how the work can be used in practice, or what is still needed to be done so the work can be useful.} \textcolor{blue}{
We thank the reviewer for suggesting this very useful reference, a citation of which has been included in the revised version of the paper.
We fully agree that there are gaps between the coarse energy model applied in our work and more detailed energy models for energy consumption is sensor networks,
e.g.\ those analyzed by Halgamuge et al.\ (2009).
These gaps, and their possible implications on practical usability of our approaches, are now discussed in the new Section 3.2.
}
\end{itemize}

\noindent
Final comment: 
Newly added parts of the paper are also in \textcolor{blue}{blue} font.
In cases where the text is restructured, but the sentences and expressions are not altered, only the section headings are in blue.

### 2018-10-11 smt/ivanova.tex
MI: some typos fixed
DH: Submitted version of the first revision.

\institute{M. Ivanova \at
              Department of Informatics, University of Bergen, Norway \\
              Tel.: +47 942 77 070\\
              \email{Marika.Ivanova@uib.no}         %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           D. Haugland \at
              Department of Informatics, University of Bergen, Norway \\
              Tel.: +47 55584033\\
              \email{Dag.Haugland@uib.no}         %  \\
}

@@

\bibitem[Halgamuge et al.(2009)]{halgamuge}
Halgamuge MN, Zukerman M, Ramamohanarao K (2009)
An estimation of sensor energy consumption.
Progress In Electromagnetics Research B 12:259--295

>>>>

\institute{M. Ivanova \at
              Department of Informatics, University of Bergen, Norway \\
              Tel.: +47 94277070\\
              \email{Marika.Ivanova@uib.no}         %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           D. Haugland \at
              Department of Informatics, University of Bergen, Norway \\
              Tel.: +47 55584033\\
              \email{Dag.Haugland@uib.no}         %  \\
}

@@

\bibitem[Halgamuge et al.(2009)]{halgamuge}
\textcolor{blue}{Halgamuge MN, Zukerman M, Ramamohanarao K (2009)
An estimation of sensor energy consumption.
Progress In Electromagnetics Research B 12:259--295}
